Type Refinements for the Working Class

### 2015-11-27 paper.tex
remove dead comment
Pluralization

Martin-L\"of's key innovation was the commitment to pervasive functionality
(extensionality) as part of the \emph{definitions} of the judgments and the
types, in contrast to the state of affairs in formal type theory where
functionality is a metatheorem which must be shown to obtain, based on the
(somewhat arbitrary) equational theory which has been imposed. Furthermore,
models for behavioral type theory interpret the types as partial equivalence
relations (PER) on only closed terms, and the meaning of the hypothetical
judgment is defined separately and uniformly in the logical relations style.

@@

%%% Now, let us consider relations on open terms; in general, it will be easiest
%%% for us to situate our constructions on relations in the presheaf topos
%%% $\Define{\widehat{\HypCat}}{\Sets^{\SCtx\times\Ctx}}$. Then, for any two
%%% objects objects $\Of{X,Y}{\widehat{\HypCat}}$, we can form the object of
%%% relations between them as $\Define{\Pow{X\times Y}}{\Omega^{X\times Y}}$.
%%%
%% . A binary relation $R_\tau$
%% between open expressions of sort $\tau$ can be thought of as a global section
%% of the exponential object
%% $\Match{\Pow{\Exprs_\tau\times\Exprs_\tau}}{\Omega^{\Exprs_\tau\times\Exprs_\tau}}$
%% of the presheaf topos $\Define{\widehat{\HypCat}}{\Sets^{\SCtx\times\Ctx}}$

>>>>

Martin-L\"of's key innovation was the commitment to pervasive functionality
(extensionality) as part of the \emph{definitions} of the judgments and the
types, in contrast to the state of affairs in formal type theory where
functionality is a metatheorem which must be shown to obtain, based on the
(somewhat arbitrary) equational theory which has been imposed. Furthermore,
models for behavioral type theory interpret the types as partial equivalence
relations (PERs) on only closed terms, and the meaning of the hypothetical
judgment is defined separately and uniformly in the logical relations style.

@@
